\documentclass[10pt]{article}
\def\authorship{Bryant Eisenbach (bje2113) \\ Chandan Kanungo (ck2749)}
\input{formatting.tex}

% CSEE 6863 Formal Verification HW/SW Systems
% Length: 1-2 pages, Due: October 27th
% Instructions:
%   Describe your project. What are the project goals? Include any relevant background.
%
%   Describe how your project relates to formal verification. In particular, explain how it 
%   relates to the main topics discussed in the course.
%
%   If your proposal includes any steps that may fail, such as using a tool on your own 
%   design or program, please include a plan-B (fallback) option. For example, a fallback 
%   option for using a tool on your own design could be extending a design that comes with the tool.
%
%   Use figures!
%
%   Important: You must disclose all sources that you intend to use. If your project is based on 
%   any of your prior work, it must be disclosed as well.

\begin{document}
    \section{Abstract}
    %DONE
    % Description of project
    \input{abstract.tex}
    
    \section{Background}
    %DONE
    % Background about each tool
    \input{llbmc-description.tex}
    \input{klee-description.tex}
    
    %DONE
    % Background about software component under test
    \input{hidusb-description.tex}
    
    \section{Project Description}

    \subsection{Project Goals}
    %DONE
    % Describe project goals
    The project seeks to test the driver mentioned above in a relevant context of proving
    that the software module meets the intended design parameters and is free of all bugs
    being tested, including concurrency and usage errors.
    We will do this by employing the two tools mentioned in order to provide as complete
    a basis as possible for identifying the software as correct.
    The comparison of the LLBMC tool with the Klee tool should allow some interesting 
    observations on the differences between Bounded Model Checking
    and the Symbolic Execution approach, and which kinds of bugs or programs may be found.
    
    \subsection{Alternative Paths}
    %DONE
    % Describe plan B
    If we are unable to create a meaningful framework for testing the driver, 
    we will resort to testing a piece of software developed by the team.
    One choice is a compiler that one of the team members (Bryant Eisenbach) has developed
    for COMS W4115 (Programming Languages and Translators) in Summer 2015 using the OCaml
    programming language (which has LLVM bindings for a compilation target).
    The use of this project is acceptable as it contains 1300 sloc and can compile to LLVM,
    which can be used by at least one of the tools.
    \par
    In case LLBMC or Klee tool does not provide to be useful we are also considering CBMC tool.
    It is a bounded model checker for C and C++ programs.
    However, CBMC is GCC-based (not LLVM), so switching to CBMC may prove more difficult 
    for our intended usage scenario.
    
    %DONE: Insert Bibliography
    \pagebreak
    \small
    \bibliography{bibliography.bib}{}
    \bibliographystyle{plain}

\end{document}
